Causal Bandits: Learning Good Interventions via Causal Inference

### 2016-02-05 causal-bandit/icml-2015/general.tex
Notation tweaks. Expand explanation after Prop. 4.

\todom{Change to $[0,1]^{\calA}$}
\begin{algorithm}[H]
\caption{General Algorithm}\label{alg:general}
\begin{algorithmic}
\STATE {\bf Input:} $T$, $\eta \in [0,1]^{|\calA|}$, $B \in [0,\infty)^{|\calA|}$
\FOR{$t \in \set{1,\ldots,T}$}
\STATE Sample action $a_t = a$ with probability $\eta$
\STATE Do action $a_t$ and observe $X_t$ and $Y_t$
\ENDFOR
\STATE For each $a \in \calA$ compute an estimate of its return:
\eq{
\forall a\in \calA \qquad \hat \mu_a = \frac{1}{T} \sum_{t=1}^T Z_a(X_t)
}
\STATE {\bf return} $\hat a^* = \argmax_a \hat \mu_a$
\end{algorithmic}
\end{algorithm}

\begin{theorem}\label{thm:general}
If Algorithm \ref{alg:general} is run with $B \in \R^{|\calA|}$ given by
\eq{
B_a = \sqrt{\frac{m(\eta)T}{\log\left(2T|\calA|\right)}}\,.
}
Then for $C = \sqrt{2} + 4$ we have
\eq{
\mu^* - \EE[\mu_I] \leq C\sqrt{\frac{m(\eta)}{T} \log\left(2T|\calA|\right)} + \frac{1}{T}\,.
}
\end{theorem}

@@

\begin{proposition}
$m(\eta^*) \leq |\calA|$.
\end{proposition}

@@

The second observation is that in the parallel bandit setting the $m(\eta)$ given in this section approximately coincides with the $m(\vec{q})$ in Eq.\ \ref{eq:m-simple}.
Recall in that setting that 
\eq{
\actions = \set{do()} \cup \set{do(X_i = j) : 1 \leq i \leq N \text{ and } j \in \set{0,1}}\,.
}
For $a = do()$ choose $\eta_a = 1/2$. 
Let $m = m(\vec{q})$ and for $a = do(X_i = j)$ let $\eta_a = \ind{\P{X_i = j} \leq 1/m} / (2m)$. 
Then it is easy to check that $m(\eta) \leq 2m$.

>>>>

\begin{algorithm}[H]
\caption{General Algorithm}\label{alg:general}
\begin{algorithmic}
\STATE {\bf Input:} $T$, $\eta \in [0,1]^{\calA}$, $B \in [0,\infty)^{\calA}$
\FOR{$t \in \set{1,\ldots,T}$}
\STATE Sample action $a_t = a$ with probability $\eta$
\STATE Do action $a_t$ and observe $X_t$ and $Y_t$
\ENDFOR
\STATE For each $a \in \calA$ compute an estimate of its return:
\eq{
\forall a\in \calA \qquad \hat \mu_a = \frac{1}{T} \sum_{t=1}^T Z_a(X_t)
}
\STATE {\bf return} $\hat a^* = \argmax_a \hat \mu_a$
\end{algorithmic}
\end{algorithm}

\begin{theorem}\label{thm:general}
If Algorithm \ref{alg:general} is run with $B \in \R^{\calA}$ given by
\eq{
B_a = \sqrt{\frac{m(\eta)T}{\log\left(2T|\calA|\right)}}\,.
}
Then for $C = \sqrt{2} + 4$ we have
\eq{
\mu^* - \EE[\mu_I] \leq C\sqrt{\frac{m(\eta)}{T} \log\left(2T|\calA|\right)} + \frac{1}{T}\,.
}
\end{theorem}

@@

\begin{proposition}\label{pro:m-bound}
$m(\eta^*) \leq |\calA|$.
\end{proposition}

@@

The second observation is that in the parallel bandit setting the $m(\eta)$ given in this section approximately coincides with the $m(\vec{q})$ in Eq.\ \ref{eq:m-simple}.
Recall in that setting that 
\eq{
\actions = \set{do()} \cup \set{do(X_i = j) : 1 \leq i \leq N \text{ and } j \in \set{0,1}}\,.
}
For $a = do()$ choose $\eta_a = 1/2$. 
\todom{Check please!}
Let $m = m(\vec{q})$ and note that there are at most $m$ pairs $(i,j)$ such that $\P{X_i = j} \leq 1/m$.
Thus, for $a = do(X_i = j)$ letting $\eta_a \propto \ind{\P{X_i = j} \leq 1/m} / (2m)$ guarantees $\eta_a \ge \frac{1}{2m}$ when $\eta_a \ne 0$.
It is then easy to check that $m(\eta) \leq 2m$ using an argument like that for Proposition~\ref{pro:m-bound}.
